---
title: "week2-lab"
format: html
---

alt=“Chart type of type of data where reason for including chart."

Markdown:
![Figure caption goes here](file/path/to/image){fig-alt="Alt text goes here"}

HTML:
<img src="file/path/to/image" alt="Alt text goes here">

Adding alt text (ggplot example)

```{r}
#| eval: true
#| echo: true
#| fig-cap: "Boxplot of penguin flipper lengths"
#| fig-alt: "A boxplot of penguin flipper lengths where Gentoo penguins have flipper lengths that are about 12% larger than Adelie or Chinstrap penguins."

library(tidyverse)
library(palmerpenguins)

ggplot(data = penguins, aes(x = species, y = flipper_length_mm)) +
  geom_boxplot(aes(color = species), width = 0.3, show.legend = FALSE) +
  geom_jitter(aes(color = species), alpha = 0.5, show.legend = FALSE, position = position_jitter(width = 0.2, seed = 0)) +
  scale_color_manual(values = c("darkorange","purple","cyan4")) +
  labs(x = "Species",
       y = "Flipper length (mm)") +
  theme_minimal()
```

A boxplot of penguin flipper lengths where Gentoo penguins have flipper lengths that are about 12% larger than Adelie or Chinstrap penguins.
Boxplot of penguin flipper lengths

Check to make sure your alt text was applied

(In Chrome) Right click on an image > Inspect to look at the underlying HTML of a webpage. You should see alt="Your alt text.". For example, right clicking on the image on slide 4 should reveal something that looks like this:

```{r}
library(ggplot2)
library(tidyverse)
library(palmerpenguins)

ggplot(data = penguins, aes(x = body_mass_g, fill = species)) +
  geom_histogram(alpha = 0.5, 
                 position = "identity") +
  scale_fill_manual(values = c("darkorange","purple","cyan4")) +
  labs(x = "Body mass (g)",
       y = "Frequency",
       title = "Penguin body masses")
```


```{r}
#install.packages("lterdatasampler")
library(lterdatasampler)
library(tidyr)
library(ggplot2)

pie_crab %>%

  ggplot(aes(y=latitude, x = size, group = latitude)) +

  geom_boxplot() +

  scale_x_continuous(breaks = seq(from = 7, to = 23, by = 2), limits = c(6.5,24))+

  scale_y_continuous(breaks = seq(from = 29, to = 43, by = 2), limits = c(29, 43.5)) +

  labs(title = "Crab carapace size (mm) by latitude")
```

